The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-03 Paper/Paper.tex
Further work on proof, some small improvements

\newcommand{\comment}[1]{-- #1 --}
\newcommand{\remove}[1]{}
\newcommand{\inn}{{\rm in}}

\newcommand{\conc}[0]{\bullet}

@@

\newcommand{\ap}[0]{\operatorname{ap}}
\newcommand{\apd}[0]{\operatorname{apd}}

@@

\newcommand{\refl}[0]{\operatorname{\textbf{refl}}}
\newcommand{\hpushout}[0]{\operatorname{\textbf{hpushout}}}
\newcommand{\hocolim}[0]{\operatorname{\textbf{hocolim}}}
\newcommand{\seg}[0]{\operatorname{\textbf{seg}}}
\newcommand{\inl}[0]{\operatorname{\textbf{inl}}}
\newcommand{\inr}[0]{\operatorname{\textbf{inr}}}
\newcommand{\glue}[0]{\operatorname{\textbf{glue}}}
\newcommand{\inc}[0]{\operatorname{\textbf{inc}}}
\newcommand{\com}[0]{\operatorname{\textbf{com}}}
\newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
\newcommand{\pt}[0]{*}

@@

With all these notions we can give the introduction, elimination and computation rules of higher inductive types.
The introduction rules for $H$ as given in Definition \ref{def:hit} are
\begin{minipage}{0.6\textwidth}
\[
c : A \> H \rightarrow H
\]
\end{minipage}
\begin{minipage}{0.4\textwidth}
\[
p_i : \prod (x : B_i \> H), t_i = r_i.
\]
\end{minipage}
We also have an elimination rule for which we use the lifting of constructor terms.
\begin{equation*}
	\AxiomC{$\vdash Y : H \rightarrow \Type$}
	\noLine
	\UnaryInfC{$\vdash f : \prod (x : A \> H), \bar{A} \> Y \> x \rightarrow Y \> (c \> x)$}
%	\noLine
	\AxiomC{$\vdash q_i : \prod (x : B_i \> H) (h_x : \bar{B}_i \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j$}
	\BinaryInfC{$\vdash H\frec(f, q_1, \ldots, q_n) : \prod (x : H), Y \> x$}
	\DisplayProof
\end{equation*}
Let us abbreviate $H\frec(f, q_1, \ldots, q_n)$ by $H\frec$.
The type $H$ also has computation rules for each point $t : A \> H$
\begin{equation*}
H\frec \> (c_i \> t) \equiv f_i \> t \> (\bar{A} \> H\frec \> t),
\end{equation*}
and for each $a : B_i \> H$
\begin{equation*}
\apd \> H\frec \> (p_j \> a) \equiv q_j \> a \> (\bar{B}_i \> H\frec \> a).
\end{equation*}
Note that these equalities are definitional rather than propositional.

@@

Next we define the homotopy pushout.
\lstset{language=Coq}
\begin{lstlisting}
Inductive $\hpushout$ $(A, B, C : \Type)$ $(f : A \rightarrow B)$ $(g : A \rightarrow C)$ :=
| $\inl$ : $B \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
| $\inr$ : $C \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
| $\glue$ : $\prod (a : A), \inl (f \> a) = \inr (g \> a)$
\end{lstlisting}
Note the similarities with the construction of the pushout.
Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
\lstset{language=Coq}
\begin{lstlisting}
Inductive $\hocolim$ $(F : \mathbb{N} \rightarrow \Type)$ $(f : \prod (n : \mathbb{N}, F \> n \rightarrow F(n+1)))$ :=
| $\inc$ : $\prod (n : \mathbb{N}), F \> n \rightarrow$ $\hocolim$ $F$ $f$
| $\com$ : $\prod (n : \mathbb{N}) (x : F \> n), \inc \> n \> x = \inc \> (n+1) \> (f \> n \> x)$
\end{lstlisting}

@@

Now we have enough to define the approximator.
During the construction one also needs to pay attention to coherency.
For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times..
By tweaking the pushout a little bit, one can easily solve these coherency problems.

\begin{definition}
Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
Then we define the \emph{approximator} $H_{\Approx}$, which has a parameters $P, Q$ and $f : H_{\Con} \> Q \rightarrow P$, of $H$ the following pushout
\[
\xymatrix
{
	((\one + \one) \times B_i \> P) + H_{\Con} \> Q \ar[d]_{\overline{t_i} + \overline{r_i} + H_{\Con}(f \circ \inn_1)} \ar[rr]^-{\delta + f} & & (I^1 \times B_i \> P) + P  \ar[d]^{\inr}\\
	H_{\Con} \> P \ar[rr]_{\inl} & & H_{\Approx} \> P \> Q \> f
}
\]
Note that this can be written as the homotopy pushout.
Often we will suppress the maps $f$ from the notation.
\end{definition}

\begin{definition}
In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows
\begin{align*}
F \> 0 &= H_{\nonrec},\\
F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0))\\
F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \qedhere
\end{align*}
For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
\[
\xymatrix@1
{
	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} P.
}
\]
Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
\end{definition}

@@

\begin{lemma}
\label{lem:colim_commute_poly}
The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \circ F) \> (A \> f)$ are isomorphic for all polynomials $A$.
\end{lemma}

\begin{proof}

\end{proof}

Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \circ F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
\[
\xymatrix
{
		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} &
		& H_{\Con}(F \> n) \ar[r]^-{\inl}
		& H_{\Approx}(F \> n) = F(n + 1)
}
\]
where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.

Next we need to show the commutativity of the following triangle.
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[rr]^{A_{\rec}(f \> n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
	& \hocolim \> F \> f &
}
\]
Before we continue, let us recall that inductive types are functors.
Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T \> f : T \> P \rightarrow T \> Q$.
Let us start with the following rectangle
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \circ \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
		& H_{\rec}(F(n+1)) \ar[rr]_{\term \circ \iota_2} &
		& H_{\Con}(F(n+1))
}
\]
The left square commutes, because by definition of $H_{\rec} \> f$ we have
\[
H_{\rec} \>(f \> n) \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> (f \> n) \> x).
\]
For a similar reason the right triangle commutes as well.
Hence, it suffices to show that the following diagram commutes.
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
		& F(n+1) \ar[d]^{f(n+1)}\\
	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
		& H_{\Approx} \> (F(n+1)) \> (F \> n)
}
\]
Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
Hence, this diagram commutes, because of the pushout we used to define $H_{\Approx}$.

@@

For this we use the eliminator of the homotopy colimit.
First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
By definition we have the following string of maps
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
}
\]
Next we need to show that the following diagram commutes.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)}\\
	I^1 \times B_i \> (F(n+1)) \ar[r]_-{\inn_1} & I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
Note that the left diagram commutes.
For the right diagram we can unpack the definition of $f(n+1)$.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
\textbf{Another coherency which should be added.}

Now we have the following diagram
\[
\xymatrix
{
	2 \times B_i(\hocolim \> F \> f) \ar[r] \ar[dr]_{\overline{t_i} + \overline{r_i}} & I^1 \times B_i(\hocolim \> F \> f) \ar[r] & \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \ar[dl]\\
	& \hocolim \> F \> f
}
\]

@@

\subsection{Elimination Rule}
For the next step we define the right eliminator for $\hocolim \> F \> f$. 
For this we suppose that we have
\[
Y : \hocolim \> F \> f \rightarrow \Type
\]
\[
c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec})
\]
\[
c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x)
\]
\[
q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j
\]
In order to make a map $\prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $\prod (x : F \> n), Y(\inc \> n \> x)$.

We start by making a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.
Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
So, let us assume that we have $a : A_{\nonrec}$.
Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec} \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
Hence, we get a map $\prod (x : F \> 0), Y(\inc \> 0 \> x)$.

Now suppose that we have a map $\prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $\prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
In order to do so, we will first look at how to extend it to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.

Let us do this in the general case.
Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $h : \prod (x : P), Y(g \> x)$.
Our goal is to extended the map into a $h' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take
\[
c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y
\]
Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
On the component $P$ it is just $h$, and on the other components we define it via extension.

Next we need to extend the map to $H_{\Approx} \> P \> Q$.
For that we need to make a map $h' : \prod (x : I^1 \times B_i \> P), Y()$

Let $(t, x) : I^1 \times B_i \> P$, and now we use $I^1$ induction.
If $t = 0$, we map it to $\hatt_i (x)$, and for $t = 1$ we map it to $\hatr_i (x)$.
Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.

For the commutativity of the diagram note that by definition the dependent map from $H_{\Con} \> P$ to $Y$ sends the constructor term $t_i$ to the lift $\hatt_i$.
This is because the map replaces each $c_{\rec}$ by $c_{Y, \rec}$ which is precisely how the lift was constructed.

Next we do it for the coherency.

Induction on the level (so, ultimately some kind of simultaneous induction?)

Then induction on the depth.

Base case: just induction assumption.

Step case: then it can be worked out from the diagram.

>>>>

\newcommand{\Boperator}[1]{\mathrm{\mathbf{#1}}}
\newcommand{\comment}[1]{-- #1 --}
\newcommand{\remove}[1]{}
\newcommand{\inn}{\Boperator{in}}

\newcommand{\conc}[0]{\bullet}
\newcommand{\comp}[0]{\circ \,}

@@

\newcommand{\ap}[0]{\operatorname{ap}}
\newcommand{\apd}[0]{\operatorname{apD}}

@@

\newcommand{\idmap}[0]{\Boperator{Id}}
\newcommand{\refl}[0]{\Boperator{refl}}
\newcommand{\hpushout}[0]{\Boperator{hpushout}}
\newcommand{\hocolim}[0]{\Boperator{hocolim}}
\newcommand{\seg}[0]{\Boperator{seg}}
\newcommand{\inl}[0]{\Boperator{inl}}
\newcommand{\inr}[0]{\Boperator{inr}}
\newcommand{\glue}[0]{\Boperator{glue}}
\newcommand{\inc}[0]{\Boperator{inc}}
\newcommand{\com}[0]{\Boperator{com}}
\newcommand{\Type}[0]{\operatorname{\textsc{Type}}}
\newcommand{\pt}[0]{*}

@@

With all these notions we can give the introduction, elimination and computation rules of higher inductive types.
The introduction rules for $H$ as given in Definition \ref{def:hit} are
\begin{minipage}{0.6\textwidth}
\[
c : A \> H \rightarrow H
\]
\end{minipage}
\begin{minipage}{0.4\textwidth}
\[
p_i : \prod (x : B_i \> H), t_i = r_i.
\]
\end{minipage}
We also have an elimination rule for which we use the lifting of constructor terms.
\begin{equation*}
	\AxiomC{$\vdash Y : H \rightarrow \Type$}
	\noLine
	\UnaryInfC{$\vdash f : \prod (x : A \> H), \bar{A} \> Y \> x \rightarrow Y \> (c \> x)$}
%	\noLine
	\AxiomC{$\vdash q_i : \prod (x : B_i \> H) (h_x : \bar{B}_i \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j$}
	\BinaryInfC{$\vdash H\frec(f, q_1, \ldots, q_n) : \prod (x : H), Y \> x$}
	\DisplayProof
\end{equation*}
Let us abbreviate $H\frec(f, q_1, \ldots, q_n)$ by $H\frec$.
The type $H$ also has computation rules for each point $t : A \> H$
\begin{equation*}
H\frec \> (c \> t) \equiv f \> t \> (\bar{A} \> H\frec \> t),
\end{equation*}
and for each $a : B_i \> H$
\begin{equation*}
\apd \> H\frec \> (p_i \> a) \equiv q_i \> a \> (\bar{B}_i \> H\frec \> a).
\end{equation*}
Note that these equalities are definitional rather than propositional.

@@

Next we define the homotopy pushout.
\lstset{language=Coq}
\begin{lstlisting}
Inductive $\hpushout$ $(A, B, C : \Type)$ $(f : A \rightarrow B)$ $(g : A \rightarrow C)$ :=
| $\inl$ : $B \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
| $\inr$ : $C \rightarrow$ $\hpushout$ $A$ $B$ $C$ $f$ $g$
| $\glue$ : $\prod (a : A), \inl (f \> a) = \inr (g \> a)$
\end{lstlisting}
Note the similarities with the construction of the pushout \cite{mac2013categories}.
Lastly, we can define the homotopy colimit as a higher inductive type in much the same way.
\lstset{language=Coq}
\begin{lstlisting}
Inductive $\hocolim$ $(F : \mathbb{N} \rightarrow \Type)$ $(f : \prod (n : \mathbb{N}, F \> n \rightarrow F(n+1)))$ :=
| $\inc$ : $\prod (n : \mathbb{N}), F \> n \rightarrow$ $\hocolim$ $F$ $f$
| $\com$ : $\prod (n : \mathbb{N}) (x : F \> n), \inc \> n \> x = \inc \> (n+1) \> (f \> n \> x)$
\end{lstlisting}

@@

Now we have enough to define the approximator.
During the construction one also needs to pay attention to coherency.
For example, in $P$ we have terms using $c_{\rec}$ at most $k$ times, so in $H_{\Approx} \> P$ we have duplicates of terms using $c_{\rec}$ less than $k$ times.
There will be several coherency problems during the proof, so the pushout will seem rather intimidating at first.

\begin{definition}
Let a higher inductive type $H$ be given as before, and let the type $H_{\Con}$ be defined as before.
Given are parameters $P$ and $Q$ with amps $i_l : H_{\Con} \> Q \rightarrow P$ and $i_r : I^1 \times B_i \> Q + Q \rightarrow P$.
Let us define the following maps.
\begin{align*}
\widetilde{i_l} &= i_l \comp \inn_1\\
g_1 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q  + (I^1 \times B_i \> Q + Q)\rightarrow (I^1 \times B_i \> P) + P\\
g_1 &= (\inn_1 \comp \delta \times \idmap) + (\inn_2 \comp i_l) + (\inn_2 \comp i_r \circ \inn_1)\\
g_2 &: ((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q + Q) \rightarrow H_{\Con} \> P + (I^1 \times B_i \> P + P)\\
g_2 &= (\inn_1 \comp \overline{t_i} + \overline{r_i})+ (\inn_1 \comp H_{\Con} \> \widetilde{i_l}) + (\inn_2 \comp (I^1 \times B_i \> \widetilde{i_l}))
\end{align*}
Then we define the \emph{approximator} $H_{\Approx}$ of $H$ the following pushout.
\[
\xymatrix
{
	((\one + \one) \times B_i \> P) + H_{\Con} \> Q + (I^1 \times B_i \> Q) 
	\ar[d]_{g_2} 
	\ar[r]^-{g_1}
	& (I^1 \times B_i \> P) + P  
	\ar[d]^-{\inr}\\
	H_{\Con} \> P + (I^1 \times B_i \> P)  
	\ar[r]_-{\inl} 
	& H_{\Approx} \> P \> Q \> i_l \> i_r
}
\]
Note that this can be written as the homotopy pushout.
Often we will suppress the maps from the notation.
\end{definition}

The types $Q$ and $P$ represent $F(n-2)$ and $F(n-1)$ respectively, and the maps $i_l$ and $i_r$ are the inclusion maps into $F(n-1)$.
The new type is extended with constructors and paths given by $\inl \comp \inn_1$ and $\inr \comp \inn_1$ respectively.
Also, there are coherency conditions added and these are given by the second and third component of the left upper corner.
Their use will become clear in the Section \ref{sec:rules} when we show the introduction rules.
Now we can define the approximating sequence.

\begin{definition}
In the setting as described, we simultaneously define a sequence of approximations $F : \mathbb{N} \rightarrow \Type$ to $H$ and maps $f : \prod(n : \mathbb{N}), F \> n \rightarrow F(n+1)$ as follows
\begin{align*}
F \> 0 &= H_{\nonrec},\\
F \> 1 &= H_{\Approx} \> (F \> 0) \> \zero \> (\zero\frec (F \> 0)) \> (\zero\frec (F \> 0))\\
F(n+2) &= H_{\Approx} \> (F(n+1)) \> (F \> n) \> \inl \> \inr \qedhere
\end{align*}
For the maps maps $f \> n : F \> n \rightarrow F(n + 1)$, note that we always have the following sequence of maps
\[
\xymatrix@1
{
	P \ar[r] & (I^1 \times B_i \> P) + P \ar[r] & H_{\Approx} P.
}
\]
Taking $P$ to be $F \> n$, then we have $F (n+1) = H_{\Approx} (F \> n)$, and thus the composition gives the map $F \> n \rightarrow F(n + 1)$.
\end{definition}

@@

\begin{lemma}
\label{lem:colim_commute_poly}
The types $A \> (\hocolim \> F \> f)$ and $\hocolim \> (A \comp F) \> (A \> f)$ are isomorphic for all polynomials $A$.
\end{lemma}

\begin{proof}
If $A$ is constant then it follows from Lemma \ref{lem:colimcon}.
For the identity it is trivial, and for sums and products, it follows from Lemmata \ref{lem:colimsum} and \ref{lem:colimprod} respectively. 
\end{proof}

Now we will construct the map $A_{\rec} \> (\hocolim \> F \> f) \rightarrow \hocolim \> F \> f$, and by Lemma \ref{lem:colim_commute_poly} it suffices to make a map $\hocolim \> (A_{\rec} \comp F) \> (A \> f) \rightarrow \hocolim \> F \> f$.
For this we use the recursion rule of $\hocolim$, and we start with the following string of maps
\[
\xymatrix
{
		A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} &
		& H_{\Con}(F \> n) \ar[r]^-{\inl}
		& H_{\Approx}(F \> n) = F(n + 1)
}
\]
where the map $H_{\rec}(F \> n) \rightarrow H_{\Con}(F \> n)$ is the inclusion and the map $H_{\Con}(F \> n) \rightarrow H_{\Approx}(F \> n)$ is the pushout map.
Composing this map with $\inc$, gives maps $A_{\rec}(F \> n) \rightarrow \hocolim \> F \> f$ for all $n : \mathbb{N}$.

Next we need to show the commutativity of the following triangle.
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[rr]^{A_{\rec}(f \> n)} \ar[dr] & & A_{\rec}(F(n+1)) \ar[dl] \\
	& \hocolim \> F \> f &
}
\]
Before we continue, let us recall that inductive types are functors.
Suppose, we have an inductive type $T$ with a parameter $P$, then a function $f : P \rightarrow Q$ gives a function $T \> f : T \> P \rightarrow T \> Q$.
Let us start with the following rectangle
\[
\xymatrix
{
	A_{\rec}(F \> n) \ar[r]^-{c_{\rec}'} \ar[d]_{A_{\rec}(f \> n)} 
		& H_{\rec}(F \> n) \ar[rr]^{\term \comp \iota_2} \ar[d]_{H_{\rec}(f \> n)} &
		& H_{\Con}(F \> n) \ar[d]_{H_{\Con}(f \> n)}\\
	A_{\rec}(F(n+1)) \ar[r]_-{c_{\rec}'} 
		& H_{\rec}(F(n+1)) \ar[rr]_{\term \comp \iota_2} &
		& H_{\Con}(F(n+1))
}
\]
The left square commutes, because by definition of $H_{\rec} \> f$ we have
\[
H_{\rec} \>(f \> n) \> (c_{\rec}' x) = c_{\rec}' (A_{\rec} \> (f \> n) \> x).
\]
For a similar reason the right triangle commutes as well.
Hence, it suffices to show that the following diagram commutes.
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[d]_{H_{\Con} \> (f \> n)} \ar[r]^-{\inl}
		& F(n+1) \ar[d]^{f(n+1)}\\
	H_{\Con}(F(n+1)) \ar[r]_-{\inl}
		& H_{\Approx} \> (F(n+1)) \> (F \> n)
}
\]
Note that $H_{\Approx}(F(n+1)) = F(n+2)$ and $H_{\Approx}(F \> n) = F(n+1)$.
Hence, this diagram commutes, because of the pushout we used to define $H_{\Approx}$.

@@

For this we use the eliminator of the homotopy colimit.
First, we need to make for all $n$ a map $I^1 \times B_i \> (F \> n)  \rightarrow \hocolim \> F \> f$.
By definition we have the following string of maps
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr}& F(n+1) \ar[rr]^-{\inc(n+1)} & & \hocolim \> F \> f.
}
\]
Next we need to show that the following diagram commutes.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) \ar[r]^-{\inn_1} \ar[d]_{I^1 \times B_i \> (f \> n)} & I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)}\\
	I^1 \times B_i \> (F(n+1)) \ar[r]_-{\inn_1} & I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
Note that the left diagram commutes.
For the right diagram we can unpack the definition of $f(n+1)$.
\[
\xymatrix
{
	I^1 \times B_i \> (F \> n) + F \> n \ar[r]^-{\inr} \ar[d]_{I^1 \times B_i \> (f \> n) + f \> n} & F(n+1) \ar[d]^{f(n+1)} \ar[dl]^{\inn_2}\\
	I^1 \times B_i \> (F(n+1)) + F(n+1) \ar[r]_-{\inr}& F(n+2) 
}
\]
On the first coordinate it commutes by definition and on the second it commutes by how $F(n+2)$ was defined.

Now we check that the defined paths have the right endpoints, and for that we look at the following diagram.
\[
\xymatrix
{
	2 \times B_i(\hocolim \> F \> f) \ar[r] \ar[dr]_{\overline{t_i} + \overline{r_i}} & I^1 \times B_i(\hocolim \> F \> f) \ar[r] & \hocolim \> (I^1 \times B_i \> F) \> (I^1 \times B_i \> f) \ar[dl]\\
	& \hocolim \> F \> f
}
\]

@@

\subsection{Elimination Rule}
For the next step we define the right eliminator for $\hocolim \> F \> f$, so suppose that we are given
\[
Y : \hocolim \> F \> f \rightarrow \Type,
\]
\[
c_{Y, \nonrec} : \prod (a : A_{\nonrec}), Y(c_{\nonrec} \> a),
\]
\[
c_{Y, \rec} : \prod (x : A_{\rec} \> \hocolim \> F \> f), \overline{A_{\rec}} \> Y \> x \rightarrow Y(c_{\rec} \> x),
\]
\[
q_{Y, i} : \prod (x : B_i \> H)(h_x : \overline{B_i} \> Y \> x), \hatt_i =_{p_j \, x} \hatr_j.
\]
In order to make a map $h : \prod (x : \hocolim \> F \> f), Y \> x$, we use the induction principle of $\hocolim \> F \> f$, and for that we first need to make maps $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$ for $n : \mathbb{N}$.

We start by making a map $h \> 0 : \prod (x : F \> 0), Y(\inc \> 0 \> x)$.
Recall that $F \> 0$ was defined to be $H_{\nonrec}$ which only has a constructor $c'_{\nonrec} : A_{\nonrec} \rightarrow H_{\nonrec}$.
So, let us assume that we have $a : A_{\nonrec}$.
Since $c_{\nonrec} \> a = \inc \> 0 \> (c_{\nonrec}' \> a)$, it suffices to find an inhabitant of $Y(c_{\nonrec} \> a)$, and for that we take $c_{Y, \nonrec} \> a$.
Hence, we get a map $h \> 0$.

Now suppose that we have a map $h \> n : \prod (x : F \> n), Y(\inc \> n \> x)$, and our goal is to make a map $h(n+1) : \prod  (x : F(n+1)), Y(\inc \> (n+1) \> x)$.
In order to do so, we will first look at how to extend $h \> n$ to a map $\prod (x : H_{\Con} (F \> n)), Y(\inc \> (n+1) \> (\inl \> x))$.

Let us do this in the general case.
Suppose, we have a map $g : P \rightarrow \hocolim \> F \> f$, and that we already constructed $\varphi : \prod (x : P), Y(g \> x)$.
Our goal is to extended the map into a $\varphi' : \prod (x : H_{\rec} P), Y(c_{Y, \rec} \> x)$, and for that we use $H_{\rec}$-induction.
Note that for each $c'_{\rec} \> x$ with $x : A_{\rec} \> P$ we have the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$, and thus we have a type family on $H_{\rec}$.
Now let $x : A_{\rec} \> P$ and $y : \overline{A_{\rec}} \> Y \> x$ be given.
Then we need to give an element of the type $Y(c_{\rec} \> (A_{\rec} \> g \> x))$ for which we take $c_{Y,\rec} \> (A_{\rec} \> g \> x) \> y$.

Now we can also extend the map to $H_{\Con}^n \> P$, because we can define this map on each component.
On the component $P$ it is just $\varphi$, and on the other components we define it via extension.

Next we need to extend the map to $H_{\Approx} \> P \> Q$.
This is done by the universal mapping property of the pushout, and that requires two steps.
First, we need to extend the map to $I^1 \times B_i \> P$, and second we need to check that the diagram given by the pushout commutes.
For that we start with $(y, x) : I^1 \times B_i \> P$, and we use $I^1$-induction.
If $y = 0$, we map it to $\hatt_i (x)$, and for $y = 1$ we map it to $\hatr_i (x)$.
Now the path $q_{Y, i}$ gives the image of $\seg$, and that finishes the induction.

Since $H_{\Approx}$ is a pushout, we also need to show that a diagram commutes.
The left upper corner is defined to be a sum, and thus it suffices to check it for each of the components.
For the first, $H_{\Con} \> P$, note that the map $\varphi'$ to $Y$ defined by extension, sends the constructor term $t_i$ to its lift $\hatt_i$, since it replaces each $c_{\rec}$ by $c_{Y, \rec}$.
On $I^1 \times B_i \> P$ the points are mapped to the lifts $\hatt_i$ as well, and thus the diagram commutes on this component.

Next we do it for the coherency condition on the points where we look at the following corner
\[
\xymatrix
{
	H_{\Con}(F \> n) \ar[r]^{\inl} \ar[d]_{H_{\Con} (f \> n)} & F(n+1)\\
	H_{\Con} (F(n+1))
}
\]
Elements of $H_{\Con}(F \> n)$ are terms built from $c_{\rec}$ on $F \> n$.
In order to show that it commutes for all inhabitants of $H_{\Con}(F \> n)$, we use induction on the depth.
If the inhabitant is of the form $\inn_1 \> x$ with $x : F \> n$, then it gets mapped to the first component of $H_{\Con} (F(n+1))$ and $F(n+1)$.
In both cases it is just mapped with $h \> (n+1)$ and thus they are equal.

To show that it holds for the other inhabitants as well, we take a look at $c_{\rec}' \> x$.
By $\inl$ it gets mapped $\inl (c_{\rec}' \> x)$.
Since $h(n+1)$ is defined as the pushout map, it maps $\inl (c_{\rec}' \> x)$ to $h \> (n+1) \> (c_{\rec}' \> x) \equiv c_{Y, \rec}(h \> n \> x)$.
The map $H_{\Con} (f \> n)$ sends $c_{\rec}' \> x$ to $c_{\rec}' (f \> n \> x)$, and the dependent map $h$ sends it to $c_{Y, \rec}(h \> (n+1) \> (f \> x))$.
Using the definition of the pushout map, this is equal to $c_{Y, \rec}(h \> n \> x)$
Hence, this diagram commutes, and thus the first coherency is fine.

Now we also need to check the second coherency, and then we look at another corner
\[
\xymatrix
{
	I^1 \times B_i (F \> n) \ar[rr]^-{\inr \circ \inn_1} \ar[d]_{I^1 \times B_i \inl} & & F(n+1)\\
	I^1 \times B_i(F(n+1)) 
}
\]
Let $(y, x) : I^1 \times B_i (F \> n)$.
Note that 
\[
h \> (n+1) \> (\inr(\inn_1 (y, x))) = h \> n \> (\inn_1 (y, x)) = \overline{q_{Y, i}}(y, h \> n \> x).
\]
\[
h \> (n+1) \> (I^1 \times B_i \> \inl \> (y, x)) = h \> (n+1) \> (y, \inl x) = \overline{q_{Y, i}}(y, h \> (n+1) \> (\inl \> x)) = \overline{q_{Y, i}}(y, h \> n \> x).
\]
Hence, this coherency is fine as well.
